Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-05-09 code/paper.Rmd
talk pages

```{r}
ten_k_random_wp_pages %>% 
  mutate(tp_divided_by_page_word_count = talk_page_wordcount / page_wordcount) %>% 
  ggplot(aes(talk_page_wordcount)) +
  geom_histogram() +
  scale_x_log10(labels = scales::comma_format(accuracy = 0.01))
```

>>>>

ten_k_random_wp_pages %>% 
  select(talk_page_wordcount) %>% 
  mutate(Site = "Random pages"),

page_data_for_all_pages %>% 
  select(talk_page_wordcount) %>% 
  mutate(Site = "World Heritage pages")
) %>%

  ggplot(aes(talk_page_wordcount, 
             fill = Site)) +
  geom_density(alpha = 0.3) +
   scale_fill_viridis_d(labels = c("Random", 
                               "World Heritage")) +
  labs(x = "Talk page word count",
       fill = "Wikipedia pages") +
  theme_minimal() +
  scale_x_log10(labels = scales::comma_format(accuracy = 1))

ggsave("figures/wh_wikpedia_pages_talk_page_worcount.png")
```

which WH pages have the longest talk pages?
